Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-02-24 paper.tex
FastR pipeline execution

        \subsection{Pipeline description}
        A pipeline in FastR is a \textit{Network} of connected \textit{Nodes} in
which the directed edges represent the flow of data.  Each \textit{node}
contains a JSON or XML template known as a \textit{Tool}.

@@

        \subsection{Pipeline execution}

>>>>

        \subsection{Pipeline description}

        A pipeline in FastR is a \textit{Network} of connected \textit{Nodes} in
which the directed edges represent the flow of data.  Each \textit{node}
contains a JSON or XML template known as a \textit{Tool}.

@@

        \subsection{Pipeline execution}
        To commence pipeline execution, the \textit{Network}'s execution
function is called on the Submission host. FastR then analyses the network and
its dependencies and breaks
down the Network into chunks that can be further processed. From the chunks, the
execution order of the \textit{Nodes} is determined.

During \textit{Node} execution, a job is created for each input/output
combination. Jobs are then executed on the execution host (i.e. local, cluster,
cloud), as determined by the execution engine plugin. FastR currently only
offers support for local and cluster plugins, however can easily be extended to
support other plugins.

While the job is executing, input URIs are translated to their actual values,
the execution environment is set up by the \textit{Tool} and the \textit{Tool}
command is executed by the \textit{Interface}. When the \textit{Interface}
returns the results, the
output data is validated and translated to URI format.

After job completion, the results are returned to the Submission Host which
reads the output and updates the network accordingly. Should a chunk be
completed, the next chunk will be processed with the updated information, until
all chunks have been processed and network execution is complete.
